Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Quasiperiodic Variables from TESS

### 2023-08-12 paper/ms.tex
update ms

A point on nomenclature.  CQVs have been called ``transient flux
dips'', ``persistent flux dips'', ``scallop shells'', ``batwings'',
\citep{2017AJ....153..152S} ``complex rotators'',
\citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}
and ``complex periodic variables'' \citep{2023MNRAS.518.2921K}.  The
CQVs should not be conflated with ``dippers'', which are classical T
Tauri stars with infrared excesses, and large-amplitude variability
linked to obscuring inner disk structures and accretion hot spots
\citep{2014AJ....147...82C,2021ApJ...908...16R}.  With that said, a
few similarities between CQVs and dippers do exist (see
Sections~\ref{subsec:irexcess} and~\ref{subsec:discdippers}).  At the
risk of introducing yet another standard, we hope to introduce a
nomenclature that reflects how, when observed over timescales of more
than tens of cycles, CQVs are almost but not exactly periodic.  They
are quasiperiodic.  While the three-type classification scheme
proposed by \citet{2017AJ....153..152S} may indeed provide some
helpful visual distinctions amongst the CQVs, it seems likely that
they are all explained by a single underlying phenomenon, and so we
opt to refer to them by a single empirically descriptive name.

@@

@@

Figure~\ref{fig:lplc} shows all available data for LP 12-502 from TESS
Sectors 18, 19, 25, 26, 53, 58, and 59, split into successive orbits.
The star was observed at 120-second cadence whenever it was observable
by TESS.  We binned the light curve to 15-minute intervals for visual
clarity, and required at least one (120-second cadence) flux
measurement per bin.  Points more than 2.5$\sigma$ above the median
are drawn in gray, also for visual clarity.  Missing data are not
drawn.  Figure~\ref{fig:lp} then shows the same data, but stacked into
successive TESS orbits spanning half a lunar month each.

@@

There is then a 6-month (184 cycle) gap to Cycles 248-315, which show
two intricately structured dip complexes, plus a small leading dip.
The single leading dip is present at the same phase as in cycles 0-64,
and is therefore likely to be the same struture.  Along a similar line
of logic, it seems plausible that the first ``dip complex'' during
cycles 248-264 represents an evolution of the initial complex seen
during cycles 0-64, though with greatly reduced depth.  During cycles
266-310, an additional local minimum develops between the two
complexes; this feature is best visualized on the river plots
(Appendix~\ref{app:lp}), and we discuss its (shorter) period below.

The second dip complex during cycles 248-315 shows the most
substructure.  During e.g.~cycles 283-298, this single complex shows
six local minima.  The deepest dip is sharp: it shows a flux excursion
of 3.5\% over about 22 minutes (0.02\,$P$), which is the steepest
slope exhibited anywhere in the LP~12-502 dataset.  After the sharp
dip, there is a roughly exponential fall-off spanning about a quarter
of a period, punctuated by coherent local minima and maxima which in
detail (Appendix~\ref{app:lp}) have slightly longer periods than the
sharp dip.  The sharp leading dip only decreases in depth following a
sudden state-switch at BTJD 2030.7 (cycles 299-315), which happens
during a flare (Figure~\ref{fig:lplc}).  The trailing dips remain
thereafter.

@@

{\sc State-switches reveal dip independence}---The state-switches seen
in cycles 1233-1247 and 299-315 confirm that dips can disappear in
less than one cycle, a point which has been previously appreciated
\citep{2017AJ....153..152S}.  What is new in these particular changes
is that the morphology changes show that the dips can be {\it
independent} and {\it additive}.  For example, throughout cycles
1233-1264, there are three local minima between phases of 0 and 0.3.
They all have identical ingress times.  The shape change during the
transition implies that the leading dip that ``turned off'' (reduced
its depth and duration), while the trailing two dips remained fixed.
In other words, the structures producing these dips are independent to
the degree that one can undergo a severe change while the others
remain essentially identical.  The state switches during cycles
248-264 and 299-315 share the same characteristic: it is always the
{\it leading} dip of a complex that ``switches off'', leaving the
(fixed-depth) trailing dips in its wake.

@@

{\sc Dip periods}---Most of the LP 12-502 dips recur with a period of
$P=18.5611 \pm 0.0001$\,hr.  However the river plots
(Appendix~\ref{app:lp}) reveal multiple distinct periodicities in the
light curve for specific dips.  For instance, in sectors 25-26, the
local minimum that develops around cycle 262 has a period faster than
the mean period by $\approx$0.1\%, while some of the trailing local
minima in the main dip complex have periods slower than the mean
period, by $\approx$0.04\%.  In addition to the fundamental period, we
were able to identify at least four distinct periods shown by specific
dips over the full Sectors 18-59 dataset, including periods at
18.5683, 18.5672, 18.5473, and 18.5145\,hr, with a typical measurement
uncertainty of $\approx$0.0002\,hr.  If each period corresponds to a
dust clump, then this implies that multiple distinct clumps can orbit
the star simultaneously, at marginally different separations.

@@

Figure~\ref{fig:catalogscatter} shows some of the derived properties
for our CQV catalog, and compares them against both the target star
sample (top panels), and against stars in the Pleiades
\citep{2016AJ....152..114R}.  Typical CQV masses span
0.1-0.4\,$M_\odot$, and typical ages span 2-150\,Myr.  This is a mass
and age regime that includes fully convective stars
($M_\star$$\lesssim$0.25\,$M_\odot$), as well as stars with radiative
cores ($M_\star$$\gtrsim$0.25\,$M_\odot$;
\citealt{2018A&A...619A.177B}).  We found no obvious morphology
differences between the two classes.  In terms of their rotation,
relative to the Pleiades, the CQVs are among the more rapidly rotating
half of M dwarfs.  The dearth of $T$$>$15.5 CQVs in our sample,
despite our search extending to $T$$=$16, is a consequence of the
120-second selection function, not detection sensitivity.

@@

The two most massive CQVs in our sample might represent an interesting
new regime, but both have ambiguities.  To date, the only stars
reported to show the CQV phenomenon are M dwarfs, with typical stellar
masses $\lesssim$0.3\,$M_\odot$
\citep{2017AJ....153..152S,2022AJ....163..144G}.  TIC~405754448 and
TIC~405910546 however appear to have masses of $\approx$0.82 and
$\approx$0.60\,$M_\odot$ respectively.  The next-highest masses in our
sample are $\approx$0.40\,$M_\odot$.  The masses for the former two
objects are consistent with their locations in the color--absolute
magnitude diagram, and with their membership in LCC.  However based on
its light curve morphology, TIC~405910546 should be studied in greater
depth, to confirm it is not an eclipsing binary.  For TIC~405754448,
we expect that the source is an unresolved binary, because RUWE$_{\rm
DR3}$=4.7, and because the raw light curves in Sectors 11, 37, and 38
for this source show an additional $\approx$6.5\,day, $\approx$0.3\%
amplitude sinusoidal signal suggestive of an unresolved photometric
companion.  If TIC~405754448 is a K+M binary, then the flux ratio
between the primary and secondary would be expected to be
$\approx$10:1.  It would be somewhat challenging for the M dwarf to
produce the observed 12.9\,hr signal with such a flux deficit, but not
impossible.  Therefore while both of these objects seem to suggest
that the CQV phenomenon may extend up in mass to pre-main-sequence K
dwarfs, more data are needed to fully substantiate this claim.

@@

TIC~425937691 is a surprising case: it shows two seemingly independent
CQV signals on what appears to be the same star.  The two signals have
periods of $\approx$4.82\,hr and $\approx$3.22\,hr, respectively.
The former is the larger amplitude signal visible in
Figures~\ref{fig:cqvs} and~\ref{fig:evoln}, corresponding to signal
with peak-to-peak amplitude of $\approx$8\%.  The latter signal is
only visible after subtracting the primary period, and it has a
sinusoidal envelope with a peak-to-peak amplitude of 2.5\%, and with
three sharp dips super-posed over each cycle.  The Gaia DR3 RUWE for
TIC~425937691 is 2.9.

@@

\section{LP 12-502}
\label{app:lp}

{\it The light curve}---
Figure~\ref{fig:lp2} shows another alternative view of
Figure~\ref{fig:lp}, but arranged to enable easy visual appreciation
of transit timing changes, rather than transit depth changes.  A
best-fitting two-harmonic sinusoid has been independently fitted and
subtracted from the Sector 18-19 data, 25-26 data, and 53, 58, and 59
data.

Finally, Figure~\ref{fig:lpriver0} shows ``river plots'' of the
same data, split into similar intervals:
the Sector 18-19 data, 25-26 data, 53 data, and 58-59 data.
State changes are evident in these plots whenever there is a sudden
change in color.
{\bf todo: fix missing data to be different from the flare color}

\begin{figure*}[!t]
	\begin{center}
    \includegraphics[width=0.45\textwidth]{ANNOTATED_resid_TIC_402980664_P18.5611_2min_phase_timegroups.png}
    	\end{center}
    \vspace{-0.4cm}
		\caption{
	      {\bf Alternative view of the evolution of LP 12-502}
	      (Figure~\ref{fig:lp}), arranged to emphasize changes in transit
	      times.  There are 200 binned black points per $P$=18.5611\,hr cycle; a two-harmonic
	      sinusoid has been subtracted from the PDC\_SAP light curve.
	      Vertical gray lines are underplotted to help guide the eye to instances
	      in which preferred dip phases synchronize over long baselines.
	      The orange and green lines guide the eye to where dips
	      change the positions of their local minima; orange
        lines have periods slightly less than $P$, the green line has
        a period greater than $P$.
		}
		\label{fig:lp2}
\end{figure*}

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.43\textwidth]{TIC402980664_river_gist_stern_0_64_manual_20230617_mask_v0_nterms2_vmin-0.04000_vmax0.01000.png}
			\includegraphics[width=0.43\textwidth]{ANNOTATED_TIC402980664_river_gist_stern_248_315_manual_20230617_mask_v0_nterms2_vmin-0.04000_vmax0.01000.png}
		}
	\vspace{-1cm}
			\subfloat{
		\includegraphics[width=0.43\textwidth]{ANNOTATED_TIC402980664_river_gist_stern_1411_1481_manual_20230617_mask_v0_nterms2_vmin-0.04000_vmax0.01000.png}
				\includegraphics[width=0.43\textwidth]{ANNOTATED_TIC402980664_river_gist_stern_1233_1265_manual_20230617_mask_v0_nterms2_vmin-0.04000_vmax0.01000.png}
	}
	\end{center}
	\vspace{-0.4cm}
	\caption{
    {\bf River plots of LP 12-502}, showing (clockwise from top-left)
    Sectors 18-19, 25-26, 53, and 58-59.  A two-harmonic sinusoid has
    been subtracted over specific chunks in time ({\bf see text}).
    For Sectors 25-26 (cycles 248-315), three periods are overplotted:
    $P$=18.5611\,hr (gray vertical line); 18.5404\,hr (orange); 18.5683\,hr (green).
    For Sector 53, gray is identical, while cyan is 18.5145\,hr.
    For Sectors 58-59, the magenta line is 18.5473\,hr, and the green
    line is 18.5672\,hr.
	}
	\label{fig:lpriver0}
\end{figure*}

@@

Figures~\ref{fig:tic3006timegroups} and~\ref{fig:tic3006river} show
120-second cadence data for TIC~300651846, a CQV in the TESS
continuous viewing zone.  If it were not for the existence of
TIC~402980664, this source would likely have been the subject of
greater attention.  With the exception of a few sectors, TESS data
will exist for TIC~300651846 over Sectors 1-12, 27-39, and 61-69.
While most of the available data will exist in the full frame images,
in Figures~\ref{fig:tic3006timegroups} and~\ref{fig:tic3006river}
focus only on the 120-second cadence data.

During Sectors 32-39, the source shows between one and four local
minima per cycle.  During the early portions of Sectors 61-65, it is
somewhat more complex, with at least five clear local minima per
cycle.  As the source evolves, this complexity decreases, while the
sharpness of one of the minima appears to increase.  We did not find
evidence for any obvious ``state-switches'' analogous to those that we
observed in LP 12-502; gradual evolution over timescales of
$\approx$50-100 cycles seem to be the norm for TIC~300651846.

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.43\textwidth]{f11a.pdf}
			\includegraphics[width=0.43\textwidth]{f11b.pdf}
		}
	\end{center}
	\vspace{-0.4cm}
	\caption{
		{\bf Long-term evolution of TIC 300651846}.
    All available 120-second cadence data as of 11 August 2023 are shown.
    Cycles 0 to 622 span TESS Sectors 32-39 (Nov 2020--June 2021);
    cycles 2296-2676 span Sectors 61-65 (Jan--June 2023).  We assumed
    a 8.254\,hr period and a fixed reference epoch (BTJD 2174.127) for
    both panels.
    Light curve segments are split based on the presence of gaps
    longer than three hours.
    Cycle numbers are listed in the lower-right of each light curve segment.
	}
	\label{fig:tic3006timegroups}
\end{figure*}

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.43\textwidth]{TIC300651846_river_seismic_0_650_vmin-0.06000_vmax0.06000.png}
			\includegraphics[width=0.43\textwidth]{TIC300651846_river_seismic_2305_2630_vmin-0.06000_vmax0.06000.png}
		}
	\end{center}
	\vspace{-0.4cm}
	\caption{
		{\bf River plots of TIC 300651846}.
		The envelope has not been subtracted.
		7 sectors of continuous 2-minute observations S32-S39.  (Thanks to DDT029)
		Then a few in S60+ on the right.
		Compare to Figure~\ref{fig:cqvs}.
	}
	\label{fig:tic3006river}
\end{figure*}

@@

TESS was the first instrument to show that CQV light curves contain
power at timescales of a few minutes
\citep{127Z,2020AJ....160...86B,2022AJ....163..144G}.  This advance
was primarily enabled by the fifteen-fold faster cadence in the TESS
2-minute data, relative to K2.

A logical follow-up question to ask is whether the periodic components
of the CQV light curves contain power at timescales below one minute.
Between 2020 and 2021, we observed 10 CQVs at 20-second cadence with
TESS in order to explore this question (TESS DDT029).  The stars were
TICs 142173958, 146539195, 24518895, 276453848, 264599508, 363963079,
144486786, 408188366, 300651846, 262400835.  The general conclusion
derived from comparing the 20-second to 120-second data for these
stars (available on MAST) was that CQVs do not contain appreciable
power at this timescale.

>>>>

A point on nomenclature.  CQVs have been called ``transient flux
dips'', ``persistent flux dips'', ``scallop shells'', ``batwings'',
\citep{2017AJ....153..152S} ``complex rotators'',
\citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}
and ``complex periodic variables'' \citep{2023MNRAS.518.2921K}.  The
CQVs should not be conflated with ``dippers'', which are classical T
Tauri stars with infrared excesses, and which show large-amplitude variability
linked to obscuring inner disk structures and accretion hot spots
\citep{2014AJ....147...82C,2021ApJ...908...16R}.  While a few
similarities between CQVs and dippers do exist (see
Sections~\ref{subsec:irexcess} and~\ref{subsec:discdippers}), their
phenomenology and stellar properties are quite different.  At the
risk of introducing yet another standard, we hope to use a
nomenclature that reflects how, when observed over timescales of more
than tens of cycles, CQVs are almost but not exactly periodic.  They
are quasiperiodic.  While the three-type classification scheme
proposed by \citet{2017AJ....153..152S} may indeed provide some
helpful visual distinctions amongst the CQVs, it seems likely that
they are all explained by a single underlying phenomenon, and so we
opt to refer to them by a single empirically descriptive name.  We
also considered names that focused on the presence of transient
corotating clumps, or more generally on circumstellar plasma tori;
for the time being, ``CQV'' seems to more accurately mirror the state
of our ignorance.

@@

%\begin{figure*}[!t]
%	\begin{center}
%		\includegraphics[width=0.45\textwidth]{ANNOTATED_resid_TIC_402980664_P18.5611_2min_phase_timegroups.png}
%	\end{center}
%	\vspace{-0.4cm}
%	\caption{
%		{\bf Alternative view of the evolution of LP 12-502}
%		(Figure~\ref{fig:lp}), arranged to emphasize changes in transit
%		times.  There are 200 binned black points per $P$=18.5611\,hr cycle; a two-harmonic
%		sinusoid has been subtracted from the PDC\_SAP light curve.
%		Vertical gray lines are underplotted to help guide the eye to instances
%		in which preferred dip phases synchronize over long baselines.
%		The orange and green lines guide the eye to where dips
%		change the positions of their local minima; orange
%		lines have periods slightly less than $P$, the green line has
%		a period greater than $P$.
%	}
%	\label{fig:lp2}
%\end{figure*}

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f10a.pdf}
			\includegraphics[width=0.48\textwidth]{f10b.pdf}
		}
	   \vspace{-0.1cm}

		\subfloat{
			\includegraphics[width=0.48\textwidth]{f10d.pdf}
			\includegraphics[width=0.48\textwidth]{f10c.pdf}
		}
	\end{center}
	\vspace{-0.4cm}
	\caption{
		{\bf River plots of the LP 12-502 light curve}, showing (clockwise from top-left)
		Sectors 18-19, 25-26, 53, and 58-59.  A two-harmonic sinusoid has
		been subtracted to highlight the sharp dips.
		In Sectors 25-26 (cycles 248-315), periods are visible at the fundamental
		period of 18.5611\,hr, as well as at faster and slower relative periods (e.g. $\phi$$\approx$0.3 and $\phi$$\approx$0.1).
		Similar instances of multiple simultaneous periods are also visible in
		Sector 53 and 58-59.
%		$P$=18.5611\,hr (gray vertical line); 18.5404\,hr (orange); 18.5683\,hr (green).
%		For Sector 53, gray is identical, while cyan is 18.5145\,hr.
%		For Sectors 58-59, the magenta line is 18.5473\,hr, and the green
%		line is 18.5672\,hr.
		White chunks denote missing data.
	}
	\label{fig:lpriver0}
\end{figure*}

@@

Figure~\ref{fig:lplc} shows all available data for LP 12-502 from TESS
Sectors 18, 19, 25, 26, 53, 58, and 59, split into successive orbits.
The star was observed at 120-second cadence whenever it was observable
by TESS.  We binned the light curve to 15-minute intervals for visual
clarity, and required at least one (120-second cadence) flux
measurement per bin.  Points more than 2.5$\sigma$ above the median
are drawn in gray, also for visual clarity.  Missing data are not
drawn.  Figure~\ref{fig:lp} then shows the same data, but stacked into
successive TESS orbits spanning half a lunar month each.
Finally, Figure~\ref{fig:lpriver0} shows ``river plots'' of the
same data, split into similar intervals:
the Sector 18-19 data, 25-26 data, 53 data, and 58-59 data.
The river plots are slightly more processed:
a maximum-likelihood two-harmonic sinusoid has been independently fitted and
subtracted from the Sector 18-19 data, 25-26 data, and 53, 58, and 59
data in order to accentuate any changes in the dip timing and structure.

@@

There is then a 6-month (184 cycle) gap to Cycles 248-315, which show
two intricately structured dip complexes, plus a small leading dip.
The single leading dip is present at the same phase as in cycles 0-64,
and is therefore likely to be the same struture.  Along a similar line
of logic, it seems plausible that the first ``dip complex'' during
cycles 248-264 represents an evolution of the initial complex seen
during cycles 0-64, though with greatly reduced depth.  During cycles
266-310, an additional local minimum develops between the two
complexes; this feature is best visualized on the river plots
(Figure~\ref{fig:lpriver0}), and we describe its (shorter) period below.

The second dip complex during cycles 248-315 shows the most
substructure.  During e.g.~cycles 283-298, this single complex shows
six local minima.  The deepest dip is sharp: it shows a flux excursion
of 3.5\% over about 22 minutes (0.02\,$P$), which is the steepest
slope exhibited anywhere in the LP~12-502 dataset.  After the sharp
dip, there is a roughly exponential fall-off spanning about a quarter
of a period, punctuated by coherent local minima and maxima which in
detail (Figure~\ref{fig:lpriver0}) have slightly longer periods than the
sharp dip.  The sharp leading dip only decreases in depth following a
sudden state-switch at BTJD 2030.7 (cycles 299-315), which happens
during a flare (Figure~\ref{fig:lplc}).  The trailing dips remain
thereafter.

@@

{\sc State-switches reveal dip independence}---The state-switches seen
in cycles 1233-1247 and 299-315 confirm that dips can disappear in
less than one cycle, a point which has been previously appreciated
\citep{2017AJ....153..152S}.  What is new in these particular changes
is that the morphology changes show that the dips can be {\it
independent} and {\it additive}.  For example, throughout cycles
1233-1264, there are three local minima between phases of 0 and 0.3.
They all have identical ingress times.  The shape change during the
transition implies that the leading dip that ``turned off'' (reduced
its depth and duration), while the trailing two dips remained fixed.
This is visible in Figure~\ref{fig:lp}.
In other words, the structures producing these dips are independent to
the degree that one can undergo a severe change while the others
remain essentially identical.  The state switches during cycles
248-264 and 299-315 share the same characteristic: it is always the
{\it leading} dip of a complex that ``switches off'', leaving the
(fixed-depth) trailing dips in its wake.

@@

{\sc Dip periods}---Most of the LP 12-502 dips recur with a period of
$P=18.5611 \pm 0.0001$\,hr.  However the river plots
(Figure~\ref{fig:lpriver0}) reveal multiple distinct periodicities in the
light curve for specific dips.  For instance, in sectors 25-26, the
local minimum that develops around cycle 262 has a period faster than
the mean period by $\approx$0.1\%, while some of the trailing local
minima in the main dip complex have periods slower than the mean
period, by $\approx$0.04\%.  In addition to the fundamental period, we
were able to identify at least four distinct periods shown by specific
dips over the full Sectors 18-59 dataset, including periods at
18.5683, 18.5672, 18.5473, and 18.5145\,hr, with a typical measurement
uncertainty of $\approx$0.0002\,hr.  If each period corresponds to an
individual dust or gas clump, then this implies that multiple distinct clumps can orbit
the star simultaneously, at marginally different separations.

@@

Figure~\ref{fig:catalogscatter} shows some of the derived stellar properties
for our CQV catalog, and compares them against both the target star
sample (top panels), and against stars in the Pleiades
\citep{2016AJ....152..114R}.  Typical CQV masses span
0.1-0.4\,$M_\odot$, and typical ages span 2-150\,Myr.  This is mass
and age includes both fully convective stars
($M_\star$$\lesssim$0.25\,$M_\odot$), and stars with a combination of radiative
cores and convective envelopes ($M_\star$$\gtrsim$0.25\,$M_\odot$;
\citealt{2018A&A...619A.177B}).  We found no obvious morphology
differences between the two classes.  In terms of their rotation,
relative to the Pleiades, the CQVs are among the more rapidly rotating
half of M dwarfs.  The dearth of $T$$>$15.5 CQVs in our sample,
despite our search extending to $T$$=$16, is a consequence of the
120-second selection function, not detection sensitivity.

@@

The two most massive CQVs in our sample might represent an interesting
new regime, but both have ambiguities.  To date, the only stars
reported to show the CQV phenomenon are M dwarfs, with typical stellar
masses $\lesssim$0.3\,$M_\odot$
\citep{2017AJ....153..152S,2022AJ....163..144G}.  TIC~405754448 and
TIC~405910546 however appear to have masses of $\approx$0.82\,$M_\odot$ and
$\approx$0.60\,$M_\odot$ respectively.  The next-highest masses in our
sample are $\approx$0.40\,$M_\odot$.  The masses for the former two
objects are consistent with their locations in the color--absolute
magnitude diagram, and with their membership in LCC.  However based on
its light curve morphology, TIC~405910546 should be studied in greater
depth, to confirm it is not an eclipsing binary.  For TIC~405754448,
we expect that the source is an unresolved binary, because RUWE$_{\rm
DR3}$=4.7, and because the raw light curves in Sectors 11, 37, and 38
for this source show an additional $\approx$6.5\,day, $\approx$0.3\%
amplitude sinusoidal signal suggestive of an unresolved photometric
companion.  If TIC~405754448 is a K+M binary, then the flux ratio
between the primary and secondary would be expected to be
$\approx$10:1.  It would be somewhat challenging for the M dwarf to
produce the observed 12.9\,hr signal with such a flux deficit, but not
impossible.  Therefore while both of these objects seem to suggest
that the CQV phenomenon may extend up in mass to pre-main-sequence K
dwarfs, more data are needed to fully substantiate this claim.

@@

TIC~425937691 is a surprising case: it shows two seemingly independent
CQV signals on what appears to be the same star.  The two signals have
periods of $\approx$4.82\,hr and $\approx$3.22\,hr, respectively.
The former is the larger amplitude signal visible in
Figures~\ref{fig:cqvs} and~\ref{fig:evoln}, corresponding to signal
with peak-to-peak amplitude of $\approx$8\%.  The latter signal is
only visible after subtracting the primary period, and it has a
sinusoidal envelope with a peak-to-peak amplitude of 2.5\%, and with
three sharp dips super-posed over each cycle.  For
TIC~425937691, ${\rm RUWE}_{\rm DR3}=2.9$.

@@

@@

Figures~\ref{fig:tic3006timegroups} and~\ref{fig:tic3006river} show
120-second cadence data for TIC~300651846, a CQV in the TESS
continuous viewing zone.  If it were not for the existence of
TIC~402980664, this source would probably have received greater
attention.  With the exception of a few sectors, TESS data will exist
for TIC~300651846 for at least Sectors 1-12, 27-39, and 61-69.  While most of
the available data will exist in the full frame images, in
Figures~\ref{fig:tic3006timegroups} and~\ref{fig:tic3006river} focus
only on the currently available 120-second cadence data.

During Sectors 32-39, the source shows between one and four local
minima per cycle.  During the early portions of Sectors 61-65, it is
somewhat more complex, with at least five clear local minima per
cycle.  As the source evolves, this complexity decreases, while the
sharpness of one of the minima appears to increase.  We did not find
evidence for any obvious ``state-switches'' analogous to those that we
observed in LP 12-502; gradual evolution over timescales of
$\approx$50-100 cycles seem to be the norm for TIC~300651846.
Unlike the TIC~402980664 river plots (Figure~\ref{fig:lpriver0}), we
did not subtract any ``continuum sinusoid'' for this source, because
the continuum is not as obviously defined.

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f11a.pdf}
			\includegraphics[width=0.48\textwidth]{f11b.pdf}
		}
	\end{center}
	\vspace{-0.4cm}
	\caption{
		{\bf Light curve evolution of TIC 300651846}.
    All available 120-second cadence data as of 2023 Aug 11 are shown.
    Cycles 0 to 622 span TESS Sectors 32-39 (Nov 2020--June 2021);
    cycles 2296-2676 span Sectors 61-65 (Jan--June 2023).  We assumed
    a 8.254\,hr period and a fixed reference epoch (BTJD 2174.127) for
    both panels.
    Light curve segments are split based on the presence of gaps
    longer than three hours.
    Cycle numbers are listed in the lower-right of each light curve segment.
	}
	\label{fig:tic3006timegroups}
\end{figure*}

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f12a.pdf}
			\includegraphics[width=0.48\textwidth]{f12b.pdf}
		}
	\end{center}
	\vspace{-0.4cm}
	\caption{
		{\bf River plots of TIC 300651846}.
    This is an alternative visualization of the data in
    Figure~\ref{fig:tic3006timegroups}.
    All available 120-second cadence data as of 2023 Aug 11 are shown.
    Cycles 0 to 622 span TESS Sectors 32-39 (Nov 2020--June 2021);
    cycles 2296-2676 span Sectors 61-65 (Jan--June 2023).  We assumed
    $P$$=$8.254\,hr and $t_0$=2174.127 [BTJD].
    Note that the two panels have slightly different color scales.
	}
	\label{fig:tic3006river}
\end{figure*}

@@

TESS was the first instrument to show that CQV light curves contain
power at timescales of a few minutes
\citep{2019A&A...625L..13Z,2022AJ....163..144G}.  This advance was
enabled by the fifteen-fold faster cadence in the TESS 2-minute data,
relative to K2.  A logical follow-up is to ask whether the periodic
components of the CQV light curves contain power at timescales below
one minute.  Between 2020 and 2021, we observed 10 CQVs at 20-second
cadence with TESS in order to explore this question (TESS DDT029).
The stars were TICs 142173958, 146539195, 24518895, 276453848,
264599508, 363963079, 144486786, 408188366, 300651846, 262400835.
These sources were selected from CQVs known at the time to have short
periods and sharp features when observed at 2-minute cadence.
Comparing the 20-second to 120-second data for these stars (data
available on MAST), we concluded that these CQVs did not contain
appreciable power at timescales shorter than a few minutes.
